%
%	Fazit
%

\pagebreak
\section{Summary}

\onehalfspacing

\subsection{Targeting}

With the demise of the ubiquitous tracking cookie, some other form of ID will evolve to support targeted or personalized advertising. It is crucial for the future of the advertising business to have some form of ability to show meaningful ads - it's advertising that powers the web.

Google FLoC is facing a lot of pushback, so we will most likely see a different method evolve over the next couple of months. It will be interesting to see how the various approaches grow and how in the end, we will see ads that matter being delivered to users.

There's a solid push to achieve a balance between the privacy needs of the users and the targeting needs of the advertisers. It is quite possible that new technology emerges that we have not seen so far - with the current technologies and the current legal framework, striking a compromise will be a difficult task and something that will keep marketeers busy for quite some time to come.

From our panelists' answers, we can see that relying on first party data is most likely a very promising strategy, as it fits nicely into the current and emerging legal frameworks. Possibly an institution will step up and regulate the use of second party data in clean rooms, but there's no indication yet that this will happen soon. On third party data, we can safely assume that the days of unfettered use are gone or will be gone soon. However, there is a possibility that machine learning algorithms will fill the void and that we're just at the beginning of a new data bonanza, with all the risks to user privacy that this might entail.

In addition, even though none of the panelists were focusing on contextual advertising, I still see contextual advertising as a very promising approach in delivering meaningful ads to users because we can do so while fully respecting the users' privacy.

Looking back at our research question from the beginning, we can conclude that working with our own first party data will be the best possible strategy in the future to place meaningful advertisements in a DS-GVO compliant way and without tracking cookies, both from a legal and a technical point of view.

\subsection{Method}

Given the volatile state of the subject in 2021, using a qualitative approach has proven very beneficial. Deviating from the classical course of categorization and employing a summative technique has also significantly contributed to the overall result and enabled us to work with a relatively small set of experts and still reach solid results.

The expert selection across a broad and diverse range of backgrounds has helped us achieve a well-rounded result; in summary, they shared a good overview of the current situation and showed us a number of possible paths forward.

The conclusions reached from the interviews were remarkably consistent and proved to be very helpful.

\subsection{Outlook}

We will see in 2022 or 2023 which direction targeted advertising will take; we can be sure, though, that it will remain an integral and vital part of the world wide web infrastructure.

A sentiment that all panelists shared was the considerable importance of first party data and its increasing role in the advertising industry - and a key takeaway for the future for all German marketeers is to become really familiar with the provisions and intricacies of the GDPR/DS-GVO and the BDSG.

\par\medskip

Happy Advertising!
